---
title: "Lab 04 - Predicting MHV Change"
subtitle: "CPP528 Group 05 Fall 2021"
author: "Cristian E. Nuno"
updated by: "Amy T. Trumpower, Melissa Millican, Sean Harrington, Joseph Papcznski"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    df_print: paged
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
# define chunk options
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE, 
                      eval = TRUE, 
                      fig.width=10)
# load necessary functions
source(here::here("analysis/utilities.R"))
```


```{r include=FALSE}
#Load the necessary packages ----
library(dplyr)
library(here)
library(knitr)
library(pander)
library(stargazer)
library(scales)
#install.packages("namespace")
#install.packages("rmarkdown")
library(rmarkdown)
library(namespace)
#set randomization seed ---
set.seed(1234)
#Load necessary functions and objects ---
#note:  all of these are R objects that will be used throughout this .rmd file
import::here("S_TYPE",
             "panel.cor",
             "cbsa_stats_df",
             "panel.smooth",
             "jplot",
             "d",
             "df",
             "dataprocessing",
             "dataw"
             .from = here::here("labs/wk04/lab_04_source.R"),
             .character_only = TRUE)
```


Today's date is `r today()`.


## Data Information


```{r}
#d <- datawrangling()

d1 <- readRDS(here::here("data/rodeo/LTDB-2010.rds"))
d2 <- readRDS(here::here("data/rodeo/LTDB-2000.rds"))
md <- readRDS(here::here("data/rodeo/LTDB-META-DATA.rds"))
d1 <- dplyr::select( d1, - year )
d2 <- dplyr::select( d2, - year )
d <- merge( d1, d2, by="tractid" )
d <- merge( d, md, by="tractid" )

#d<- dataprocessing(d)

# filter rural districts
d <- dplyr::filter( d, urban == "urban" )
#keep a set of data for backup
d.bkup <- d

d <- dplyr::select( d, tractid, 
             mhmval00, mhmval12, 
             hinc00, 
             hu00, vac00, own00, rent00, h30old00,
             empclf00, clf00, clf12, unemp00,unemp12, prof00,  
             dpov00, npov00,
             ag25up00, hs00, col00, 
             pop00.x, nhwht00, nhblk00, hisp00, asian00, empclf12, vac10, hinc12,hu12,
             h30old00, h30old12,rent10,
             cbsa, prof12, cbsaname ) %>% 
  filter(clf00 !=0, clf12 !=0, empclf00 !=0, empclf12 !=0) %>% na.omit()

d <- 
  d %>%
  dplyr::mutate( p.white = 100 * nhwht00 / pop00.x,
          p.black = 100 * nhblk00 / pop00.x,
          p.hisp = 100 * hisp00 / pop00.x, 
          p.asian = 100 * asian00 / pop00.x,
          p.hs = 100 * (hs00+col00) / ag25up00,
          p.col = 100 * col00 / ag25up00,
          p.prof00 = 100 * prof00 / empclf00,
          p.prof10 = 100 * prof12/empclf12,
          p.unemp = 100 * unemp00 / clf00,
          p.unemp10 = 100 * unemp12/clf12,
          p.vacant = 100 * vac00 / hu00,
          p.vacant10 = 100 * vac10/hu12,
          mhv.change.00.to.10 = mhmval12 - mhmval00,
          p.mhv.change = 100 * (mhmval12 - mhmval00) / mhmval00,
          p.income.change = 100 * (hinc12 - hinc00)/hinc00,
          p.30year.change = 100 * (h30old12 - h30old00)/h30old00,
          p.prof.change = 100 * (prof12 - prof00)/prof00,
          p.rent = 100 * rent00/hu00,
          p.rent10 = 100 * rent10/hu12,
          pov.rate = 100 * npov00 / dpov00 ) %>% filter(p.vacant != "NaN", p.vacant10 != "NaN",
                                                      p.unemp != "-Inf") %>% na.omit()
# inflation rate
INFLATION_RATE <- 1.28855 
# adjust 2000 home values for inflation 
mhv.00 <- d$mhmval00 * INFLATION_RATE 
mhv.10 <- d$mhmval12
# change in MHV in dollars
mhv.change <- mhv.10 - mhv.00
# drop low 2000 median home values
# to avoid unrealistic growth rates.
#
# tracts with homes that cost less than
# $10,000 are outliers
mhv.00[ mhv.00 < 10000 ] <- NA
# change in MHV in percent
mhv.growth <- 100 * ( mhv.change / mhv.00 )
d$mhv.00 <- mhv.00
d$mhv.10 <- mhv.10
d$mhv.change <- mhv.change
d$mhv.growth <- mhv.growth 
d$mhv.growth [mhv.growth > 200] <- NA
```


## Census Variables
###  The following factors were chosen to identify gentrification:
- Household Income: An increase in household income may indicate gentrification
- Percentage unemployed: a decrease in unemployment rate may indicate gentrification
- Vacancy Rate: A decrease in vacancy rate may indicate gentrification

```{r}
#Household Income
hinc.00 <- d$hinc00 * 1.28855
hinc.10 <- d$hinc12
hinc.change <- hinc.10 - hinc.00
p.hinc.change <- hinc.change/hinc.00
p.hinc.growth <- log10(p.hinc.change +1)
d$hinc.change <- p.hinc.change
d$hinc.growth <- p.hinc.growth
```

```{r}
#% Unemployed 
#d$p.unemp[ d$p.unemp > 80 & d$p.unemp <= 1 ] <- NA
#d$p.unemp10[ d$p.unemp10 > 80 & d$unemp.00 <= 1 ] <- NA
unemp.00 <- d$p.unemp
unemp.10 <- d$p.unemp10
unemp.change <- unemp.10 - unemp.00
p.unemp.change <- unemp.change/unemp.00
p.unemp.growth <- log10(p.unemp.change +1)
d$unemp.change<- p.unemp.change
d$unemp.change[d$unemp.change > 80 | d$unemp.change < 1] <- NA
d$unemp.growth  <- p.unemp.growth
d$unemp.growth[d$unemp.growth > 80 | d$unemp.growth < 1] <- NA
```


```{r}
#Vacancy Rate 
vacant.00 <- d$p.vacant
vacant.10 <- d$p.vacant10
vacant.change <- vacant.10 - vacant.00
p.vacant.change <- vacant.change/vacant.00
p.vacant.growth <- log10(p.vacant.change + 1)
d$vacant.change <- p.vacant.change
d$vacant.change[d$vacant.change > 80 | d$vacant.change < 1] <- NA
d$vacant.growth <- p.vacant.growth
d$vacant.growth[d$vacant.growth > 80 | d$vacant.growth < 1] <- NA
```


# create mini data frame
```{r}
df <- data.frame( MedianHomeValue2000=mhv.00, 
                  MedianHomeValue2010=mhv.10, 
                  MHV.Change.00.to.10=mhv.change,
                  MHV.Growth.00.to.12=mhv.growth,
                  Vacant2000 = vacant.00,
                  Vacant2010 = vacant.10,
                  Vacant.change = p.vacant.change,
                  Vacant.growth = p.vacant.growth,
                  Unemp2000 = unemp.00,
                  Unemp2010 = unemp.10,
                  Unemp.change = p.unemp.change,
                  Unemp.growth = p.unemp.growth,
                  Income2000 = hinc.00,
                  Income2010 = hinc.10,
                  Income.change = p.hinc.change,
                  Income.growth = p.hinc.growth)
df$Vacant.growth[df$Vacant.growth > 80 | df$Vacant.growth < 1] <- NA
df$Vacant.change[df$Vacant.change > 80 | df$Vacant.change < 1] <- NA
df$Unemp.change[df$Unemp.change > 80 | df$Unemp.change < 1] <- NA
df$Unemp.growth[df$Unemp.growth > 80 | df$Unemp.growth < 1] <- NA
                  
```

## Measurement Variables


```{r}
#Correlation check
measurement.1 <- select(df, Vacant2000, Income2000, Unemp2000, MedianHomeValue2000) %>% na.omit ()
```


```{r}
set.seed(1234)

pairs(measurement.1, lower.panel = panel.smooth, upper.panel = panel.cor)
```

```{r}
measurement.2 <- select(df, Vacant.change, Income.change, Unemp.change, MHV.Change.00.to.10) %>% na.omit ()
```

```{r}
set.seed(1234)

pairs(measurement.2, lower.panel = panel.smooth, upper.panel = panel.cor)
```

## Median Home Value

```{r}
hist( df$MedianHomeValue2000, breaks=200, xlim=c(0,500000), 
      col="gray20", border="white",
      axes=F, 
      xlab="MHV (median = $138k)",
      ylab="",
      main="Median Home Value in 2000 (2010 US dollars)" )
axis( side=1, at=seq(0,500000,100000), 
      labels=c("$0","$100k","$200k","$300k","$400k","$500k") )
abline( v=median( df$MedianHomeValue2000, na.rm=T ), col="orange", lwd=3 )
```



### Descriptives

```{r}
stargazer( df, 
           type="html", #S_TYPE, 
           digits=0, 
           summary.stat = c("min", "p25","median","mean","p75","max") )
```

### Change in MHV 2000 - 2010

```{r}
hist( df$MHV.Change.00.to.10/1000, breaks=500, 
      xlim=c(-100,500), yaxt="n", xaxt="n",
      xlab="Thousand of US Dollars (adjusted to 2010)", cex.lab=1.5,
      ylab="", main="Change in Median Home Value 2000 to 2010",
      col="gray20", border="white" )
axis( side=1, at=seq( from=-100, to=500, by=100 ), 
      labels=paste0( "$", seq( from=-100, to=500, by=100 ), "k" ) )
        
mean.x <- mean( df$MHV.Change.00.to.10/1000, na.rm=T )
abline( v=mean.x, col="darkorange", lwd=2, lty=2 )
text( x=200, y=1500, 
      labels=paste0( "Mean = ", dollar( round(1000*mean.x,0)) ), 
      col="darkorange", cex=1.8, pos=3 )
median.x <- median( df$MHV.Change.00.to.10/1000, na.rm=T )
abline( v=median.x, col="dodgerblue", lwd=2, lty=2 )
text( x=200, y=2000, 
      labels=paste0( "Median = ", dollar( round(1000*median.x,0)) ), 
      col="dodgerblue", cex=1.8, pos=3 )
```


### Percent Change in Median Home Value 2000 to 2010

```{r}
hg <-
hist( df$MHV.Growth.00.to.12, breaks=5000, 
      xlim=c(-100,200), yaxt="n", xaxt="n",
      xlab="", cex.main=1.5,
      ylab="", main="Growth in Home Value by Census Tract 2000 to 2010",
      col="gray40", border="white" )
axis( side=1, at=seq( from=-100, to=200, by=50 ), 
      labels=paste0( seq( from=-100, to=200, by=50 ), "%" ) )
ymax <- max( hg$count )
        
mean.x <- mean( df$MHV.Growth.00.to.12, na.rm=T )
abline( v=mean.x, col="darkorange", lwd=2, lty=2 )
text( x=100, y=(0.5*ymax), 
      labels=paste0( "Mean = ", round(mean.x,0), "%"), 
      col="darkorange", cex=1.8, pos=4 )
median.x <- median( df$MHV.Growth.00.to.12, na.rm=T )
abline( v=median.x, col="dodgerblue", lwd=2, lty=2 )
text( x=100, y=(0.6*ymax), 
      labels=paste0( "Median = ", round(median.x,0), "%"), 
      col="dodgerblue", cex=1.8, pos=4 )
```

## Metro Level Statistics

```{r include=FALSE}
cbsa_stats_df %>% head()
```


#### Metro Demographics

**Vacancy Rate**

```{r echo=FALSE}
#Vacancy Rate 2000 and 2010
par( mfrow=c(2,2) )
hist( df$Vacant2000, breaks= 150, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", xlim = c(-5,40), main="Percent of Vacancy 2000",)
hist( log(df$Vacant2000+1), breaks= 150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Percent of Vacancy 2000 (logged)")
hist( df$Vacant2010, breaks= 900, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", xlim = c(-5,40), main="Percent of Vacancy 2010",)
hist( log(df$Vacant2010 +1), breaks= 150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Percent of Vacancy 2010 (logged)")
```

```{r echo=FALSE}
#Vacancy Change
par( mfrow=c(1,2) )
hist( df$Vacant.change, breaks= 300, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(0,10), main="Percent of Vacancy from 2000 to 2010",)
hist( log(df$Vacant.change + 1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(0,3), main="Percent of Vacancy from 2000 to 2010(logged)")
```


**Unemployment Rate**

```{r echo=FALSE}
#Unemployment Rate 2000 and 2010
par( mfrow=c(2,2) )
hist( df$Unemp2000, breaks=150, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", xlim= c(-5,40), main="Percent of Unemployment 2000",)
hist( log(df$Unemp2000+1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Percent of Unemployment 2000 (logged)")
hist( df$Unemp2010, breaks=150, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", xlim= c(-5,40), main="Percent of Unemployment 2010",)
hist( log(df$Unemp2010 +1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Percent of Unemployment 2010 (logged)")
```


```{r echo=FALSE}
#Unemployment Change
par( mfrow=c(1,2) )
hist( df$Unemp.change, breaks= 200, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(0,10), main="Percent of Unemp. Change from 2000 to 2010",)
hist( log(df$Unemp.change + 1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(0,4),main="Logged")
```


**Household Income**

```{r echo=FALSE}
#Household Income 2000 and 2010
##These were labeled as % of Household income....is that right?
par( mfrow=c(2,2) )
hist( df$Income2000, breaks=150, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", main="Household Income 2000",)
hist( log(df$Income2000 +1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Income 2000 (logged)")
hist( df$Income2010, breaks=150, col="gray20", border="white", 
      yaxt="n", xlab="", ylab="", main="Household Income 2010",)
hist( log(df$Income2010 +1), breaks=150, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Household Income 2010 (logged)")
```


```{r echo=FALSE}
#Household Income Change
par( mfrow=c(1,2) )
hist( df$Income.change, breaks= 500, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(-1,2), main="% of Household Income Change 2000 to 2010",)
hist( log(df$Income.change + 1), breaks=500, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", xlim = c(-1,1), main="Logged")
```


**Correlation between MHV and Vacancy Rates**

```{r}
jplot( df$Vacant.change, df$MHV.Growth.00.to.12, ylim=c(-50,100),
       lab1="Vacancy Rates", lab2="MHV Growth" )
```
```{r}
jplot( df$Unemp.change, df$MHV.Growth.00.to.12, ylim=c(-50,100),
       lab1="Unemployment Rates", lab2="MHV Growth" )
```

```{r}
jplot( df$Income.growth, df$MHV.Growth.00.to.12, ylim=c(-50,100),
       lab1="Household Income Change(logged)", lab2="MHV Growth" )
```



## Including regression output

```{r regression, results='asis'}
# load necessary packages ----
library(stargazer)
# load constants ----
STARGAZER_OUTPUT_TYPE = "text"
# create model ----
reg.data <- d
reg.data$mhv.growth[ reg.data$mhv.growth > 200 ] <- NA
reg.data$p.unemp <- log10( reg.data$unemp.change + 1 )
reg.data$p.vacant <- log10( reg.data$vacant.change + 1 )
reg.data$p.hinc <- log10( reg.data$hinc.change + 1 )
m1 <- lm( mhv.growth ~  p.hinc, data=reg.data )
m2 <- lm( mhv.growth ~  p.unemp, data=reg.data )
m3 <- lm(mhv.growth ~ p.vacant, data = reg.data)
m4 <- lm( mhv.growth ~  p.hinc + p.unemp + p.vacant, data=reg.data )
# display model
stargazer( m1, m2, m3, m4,
           type="text", #S_TYPE,
           digits=2,
           omit.stat = c("rsq","f") )
```


## Group Structure

```{r}
d5 <- filter( d, cbsaname %in% 
                c("Tyler, TX",
                  "Minneapolis-St. Paul-Bloomington, MN-WI",
                  "San Francisco-San Mateo-Redwood City,CA") )
d5$cbsaname <- factor( d5$cbsaname, labels=c("MSP-MN","SF-CA","Tyler-TX") )
par( mar=c(4,6,4,6), mfrow=c(1,2) )
plot( d5$cbsaname,  d5$mhv.00, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Home Values in 2000" )
abline( h=seq(0,1200000,100000), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
plot( d5$cbsaname,  d5$p.unemp, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Unemployment Rates in 2000" )
abline( h=seq(0,15,1), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
```

**Vacancy 2000 Metro Level**

```{r}
d5 <- filter( d, cbsaname %in% 
                c("Tyler, TX",
                  "Minneapolis-St. Paul-Bloomington, MN-WI",
                  "San Francisco-San Mateo-Redwood City,CA") )
d5$cbsaname <- factor( d5$cbsaname, labels=c("MSP-MN","SF-CA","Tyler-TX") )
par( mar=c(4,6,4,6), mfrow=c(1,2) )
plot( d5$cbsaname,  d5$mhv.00, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Home Values in 2000" )
abline( h=seq(0,1200000,100000), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
plot( d5$cbsaname,  d5$p.vacant, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Vacant in 2000" )
abline( h=seq(0,15,1), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
```

**Household Income Metro Level**
```{r}
d5 <- filter( d, cbsaname %in% 
                c("Tyler, TX",
                  "Minneapolis-St. Paul-Bloomington, MN-WI",
                  "San Francisco-San Mateo-Redwood City,CA") )
d5$cbsaname <- factor( d5$cbsaname, labels=c("MSP-MN","SF-CA","Tyler-TX") )
par( mar=c(4,6,4,6), mfrow=c(1,2) )
plot( d5$cbsaname,  d5$mhv.00, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Home Values in 2000" )
abline( h=seq(0,1200000,100000), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
plot( d5$cbsaname,  d5$hinc00, las=1, frame.plot=F, outline=F,
      xlab="", ylab="", main="Household Income in 2000" )
abline( h=seq(0,15,1), lty=3, col=gray(0.5,0.3) )
axis( side=4, las=1 )
```




**Health of City 2000 to 2010 Grouped**

```{r}
d5 <- filter( d, cbsaname %in%
                c("Tyler, TX",
                  "Youngstown-Warren-Boardman, OH-PA",
                  "Syracuse, NY") )
d5$mhv.growth[ d5$mhv.growth > 200 ] <- NA
d5$p.unemp <- log10( d5$p.unemp + 1 )
x <- rnorm( nrow(d5), 0, 0.1 ) +
     as.numeric( d5$cbsaname == "Tyler, TX" ) + 
     2 * as.numeric( d5$cbsaname == "Youngstown-Warren-Boardman, OH-PA" ) + 
     3* as.numeric( d5$cbsaname == "Syracuse, NY" ) 
par( mfrow=c(1,2) )
plot( x, d5$mhv.growth, 
      pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      ylim=c(-50,50),
      xaxt="n", 
      ylab="", xlab="",
      main="MHV Growth")
axis( side=1, at=1:3, labels=c("Tyler","Youngstown","Syracuse"), 
      tick=F, col.axis="gray60", cex.axis=1.3 )
plot( x, d5$p.unemp, 
      pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      # ylim=c(0,40),
      xaxt="n", 
      ylab="", xlab="",
      main="Unemployment (logged)")
axis( side=1, at=1:3, labels=c("Tyler","Youngstown","Syracuse"), 
      tick=F, col.axis="gray60", cex.axis=1.3 )
```




```{r}
d5 <- filter( d, cbsaname %in%
                c("Tyler, TX",
                  "Youngstown-Warren-Boardman, OH-PA",
                  "Syracuse, NY") )
d5$mhv.growth[ d5$mhv.growth > 200 ] <- NA
#d5$p.vacant <- log10( d5$p.vacant + 1 )
x <- rnorm( nrow(d5), 0, 0.1 ) +
     as.numeric( d5$cbsaname == "Tyler, TX" ) + 
     2 * as.numeric( d5$cbsaname == "Youngstown-Warren-Boardman, OH-PA" ) + 
     3* as.numeric( d5$cbsaname == "Syracuse, NY" ) 
par( mfrow=c(1,2) )
plot( x, d5$mhv.growth, 
      pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      ylim=c(-50,50),
      xaxt="n", 
      ylab="", xlab="",
      main="MHV Growth")
axis( side=1, at=1:3, labels=c("Tyler","Youngstown","Syracuse"), 
      tick=F, col.axis="gray60", cex.axis=1.3 )
plot( x, d5$p.vacant, 
      pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      # ylim=c(0,40),
      xaxt="n", 
      ylab="", xlab="",
      main="Vacant")
axis( side=1, at=1:3, labels=c("Tyler","Youngstown","Syracuse"), 
      tick=F, col.axis="gray60", cex.axis=1.3 )
```







**Baseline metro-level home value growth**

```{r}
m <- lm( mhv.growth ~ factor(cbsaname) + p.unemp - 1, data=d5 )
b0.syracuse   <- m$coefficients[1] 
b0.tyler      <- m$coefficients[2] 
b0.youngston  <- m$coefficients[3] 
b1            <- m$coefficients[4] 
palette( c( "steelblue", "green3", "darkorange"  ) )
palette( adjustcolor( palette(), alpha.f = 0.3 ) )
plot( d5$p.unemp, d5$mhv.growth,
        pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      ylim=c(-50,50),
      xlab="Unemployment Rate (logged)",
      ylab="Median Home Value Growth 2000-2010")
          
abline( b0.syracuse, b1, col="steelblue", lwd=3 )
abline( b0.tyler, b1, col="green3", lwd=3 )
abline( b0.youngston, b1, col="darkorange", lwd=3 )
```


```{r}
m <- lm( mhv.growth ~ factor(cbsaname) + p.vacant, data=d5 )
b0.syracuse   <- m$coefficients[1] 
b0.tyler      <- m$coefficients[2] 
b0.youngston  <- m$coefficients[3] 
b1            <- m$coefficients[4] 
palette( c( "steelblue", "green3", "darkorange"  ) )
palette( adjustcolor( palette(), alpha.f = 0.3 ) )
plot( d5$p.unemp, d5$mhv.growth,
        pch=19, cex=1.5, bty = "n",  
        col=factor(d5$cbsa),
      ylim=c(-50,50),
      xlab="Vacant",
      ylab="Median Home Value Growth 2000-2010")
          
abline( b0.syracuse, b1, col="steelblue", lwd=3 )
abline( b0.tyler, b1, col="green3", lwd=3 )
abline( b0.youngston, b1, col="darkorange", lwd=3 )
```






**Adding fixed effect**

```{r}
d.reg <- d
d.reg$mhv.growth[ d.reg$mhv.growth > 200 ] <- NA
d.reg$p.unemp <- log10( d.reg$p.unemp + 1 )
# average growth in median home value for the city
d.reg <- 
  d.reg %>%
  group_by( cbsaname ) %>%
  mutate( metro.mhv.growth = 100 * median( mhv.growth, na.rm=T ) ) %>%
  ungroup() 
m1 <- lm( mhv.growth ~ unemp.change + vacant.change + hinc.change, data=d.reg )
m2 <- lm( mhv.growth ~ unemp.change + vacant.change + hinc.change + metro.mhv.growth, data=d.reg )
m3 <- lm( mhv.growth ~ unemp.change + vacant.change + hinc.change + cbsa, data=d.reg )
stargazer( m1, m2, m3, 
           type="text", #S_TYPE,
           digits=2,
           omit.stat = c("rsq","f"),
           omit="cbsa",
           add.lines = list(c("Metro Fixed Effects:", "NO", "NO","YES")) )
```